Exploring probability distributions for bivariate temporal granularities

### 2020-01-28 main.Rmd
visulaisation section minor changes

The grammar of graphics introduced a framework to incorporate underlying features for statistical graphics to construct them by relating data space to the graphic space [@Wilkinson1999-nk]. 
The layered grammar of graphics proposed by [@Wickham2009-pk], which is a modification over the former, suggests that graphics are made up of distinct layers of grammatical elements. There are seven grammatical elements in total, out of which data, aesthetics and geometries are essential elements. Data are observations made on a number of variables, typically thought of as a sample from a population distribution. Aesthetic mapping describes how variables are mapped to elements of the plot, such as horizontal axis or color. Geometries determine the physical representation of the data in the plot. The remaining grammatical elements of a graphic namely facets, statistics, coordinates and themes are optional and contains detail of the plot. Facets dictates how to split up our plot and is a powerful tool for exploratory data analysis as we can rapidly compare patterns in different parts of the data and can see whether they are the same or different.

@@

Choice of plots are dictated by the statistical transformations and geometric objects used for the visualization. The basic plot choice for our data structure is the one that can display densities. In Section \ref{sec:measured-variable}, it is discussed that these densities could be estimated using Kernel density estimates or some descriptive statistics. The latter do not allow us to see the shape, skewness, nature of the tail or multi-modality with so much clarity as the former. However, they avoid much clutter and help us to focus on some specific properties of the data. Kernel density estimates provide more detailed information about the distribution but depend on smoothing parameters and hence can vary for the same data set. In practice, the densities are estimated reasonably with at least 30 observations. However, even with large sample size, choosing too large a value for bandwidth can cause the estimate to oversmooth the data. The summaries based on descriptive statistics remain free of any tuning parameters or Kernels, which is sometimes more desirable for exploration.

>>>>

The grammar of graphics introduced a framework to construct statistical graphics by relating data space to the graphic space [@Wilkinson1999-nk]. The layered grammar of graphics proposed by [@Wickham2009-pk], which is an alternate and modified parametrization of the grammar suggests that graphics are made up of distinct layers of grammatical elements. There are seven grammatical elements in total, out of which data, aesthetics and geometries are essential elements. Data are observations made on a number of variables, typically thought of as a sample from a population distribution. Aesthetic mapping describes how variables are mapped to elements of the plot, such as horizontal axis or color. Geometries determine the physical representation of the data in the plot. The remaining grammatical elements of a graphic namely facets, statistics, coordinates and themes are optional and contains detail of the plot. Facets dictates how to split up our plot and is a powerful tool for exploratory data analysis as we can rapidly compare patterns in different parts of the data and can see whether they are the same or different.

@@

Choice of plots are dictated by the statistical transformations and geometric objects used for the visualization. The basic plot choice for our data structure is the one that can display densities. In Section \ref{sec:measured-variable}, it is discussed that these densities could be estimated using Kernel density estimates or some descriptive statistics. Kernel density estimates provide more detailed information about the distribution but depend on smoothing parameters and hence can vary for the same data set. The descriptive statistics based methods do not allow us to see the shape, skewness, nature of the tail or multi-modality with so much clarity as the former. However, they avoid clutter and help us to focus on some specific properties of the data. Also, the summaries based on descriptive statistics remain free of any tuning parameters or Kernels, which is sometimes more desirable for exploration.

<!--  However, even with large sample size, choosing too large a value for bandwidth can cause the estimate to oversmooth the data. -->
